---
title: "Walk through"
author: "Alison Hill"
date: "11/11/2020"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

```{r, include=FALSE}
source("functions.R", local = knitr::knit_global())
```


## Exploration 

```{r}
a11y <- read_theme("https://github.com/rstudio/distill/raw/master/inst/rmarkdown/templates/distill_article/resources/a11y.theme")
#a11y <- read_theme("themes/a11y_v2.theme")
#a11y <- read_theme("themes/a11y_v3.theme")

bg <- "#f8f8f8"
col <- a11y %>%
  group_by(fg) %>%
  summarise(abbr = paste(abbr, collapse = "/"), .groups = "drop") %>%
  filter(!is.na(fg)) %>% 
  mutate(contrast = contrast_ratio(fg, bg))

col %>% plot_uv()

col %>% plot_cl()

col %>% 
  arrange(contrast)

plot(prismatic::color(col$fg), labels = TRUE)
```

## Consolidate colors -> `col2`

```{r}
col2 <- col %>%
  filter(!abbr %in% c("op", "pp", "do", "cn", "ss", "at")) %>% 
  mutate(fg_before2 = fg) %>% 
  mutate(fg = ifelse(abbr == "er/al", "#d91e18", fg)) %>% 
  mutate(contrast = contrast_ratio(fg, bg))

plot(prismatic::color(col2$fg), labels = TRUE)
```

## Problems now:

1. `a11y` deep cerulean (`#007faa`) is not high enough contrast with `#f8f8f8` background color

    ```{r}
    col2 %>% filter(contrast < 4.5)
    ``` 


1. `va` is too close to `fu/op` (two blues)

1. Lightness: adjust to about 40?

1. Colorfulness: colors with similar chroma values will look less jarring

1. green + red = xmas?



## Adjust lightness -> `col3`

Stabilize lightness of colors - this means that none of the hex values match the original a11y hex colors anymore

```{r}
col2 %>% filter(contrast < 4.5)

col3 <- col2 %>%
  mutate(
    fg_before3 = fg, 
    fg = modify_hcl(fg, l = 40),
    contrast = contrast_ratio(fg, bg)
  ) 

col3 %>% pull(contrast) %>% sort() %>% round(1)

col3 %>% plot_uv()

plot(prismatic::color(col3$fg), labels = TRUE)
```

## Make colors more distinct -> `col4`

AKA questioning all the decisions thus far

1. `va` is too close to `fu/op`

    + make `fu/op` more negative on `v` channel? (done, -> `#4452C4`)

    + move `va` more positive on `u` channel?

1. make colours further apart - e.g. switch `bn/fl/dv` with `dt` (done)

```{r}
keepers <- c("bn/fl/dv", "ot/cf/kw")
col4 <- col3 %>%
  # save old fg
  mutate(fg_before4 = fg) %>% 
  # replace the grey
  mutate(fg = ifelse(abbr == "an/in/wa/co/cv", 
                     "#5E5E5E", 
                     fg)) %>% 
  # replace the red
  mutate(fg = ifelse(abbr == "er/al", 
                     "#BD1600", 
                     fg)) %>% 
  # replace the green 
  mutate(fg = ifelse(abbr == "st/vs/ch/sc", 
                     "#006E4C", 
                     fg)) %>% 
  # replace the cobalt 
  mutate(fg = ifelse(abbr == "fu", 
                     "#4452C4", 
                     fg)) %>%   
  # switch `bn/fl/dv` with `dt`
  mutate(fg = ifelse(abbr == "bn/fl/dv", "#954A00", fg)) %>% 
  mutate(fg = ifelse(abbr == "dt", "#B12458", fg)) %>%
  # replace va
  mutate(
    fg = ifelse(abbr == "va", 
                modify_hcl(fg, h = 290), fg),
    fg = ifelse(abbr == "va", 
                set_channel(fg, "u", 50, space = "Luv"), fg)
    #fg = ifelse(abbr == "va", 
                #set_channel(fg, "v", -75, space = "Luv"), fg)
  ) %>% 
  # lighten again
  mutate(
    fg = ifelse(!(abbr %in% keepers), 
                modify_hcl(fg, l = 40), 
                fg),
    contrast = contrast_ratio(fg, bg)
  ) %>% 
  # last switcheroo
  mutate(fg = ifelse(abbr == "bn/fl/dv", "#9D2E93", fg)) %>% 
  mutate(fg = ifelse(abbr == "va", "#954A00", fg))
  
col4 %>% plot_uv()

plot(prismatic::color(col4$fg), labels = TRUE)

hues_4 <- col4 %>%
  mutate(hcl(fg)) %>% 
  pull(h)

colorspace::max_chroma(h = hues_4, l = 40)

hues_4 <- col4 %>%
  mutate(hcl(fg)) %>% 
  mutate(max_c = colorspace::max_chroma(h, l = 40)) %>% 
  mutate(max_hex = farver::encode_colour(
    cbind(h, max_c, l), from = "hcl")
    )

plot(prismatic::color(hues_4$max_hex), labels = TRUE)
```

+ feels like need to choose between those last 3 colors- all too close #BC1500 -> #B12458

+ also feels like lightness correction overcorrects for chelsea gem and deep cerulean, would rather keep those as fg_before4 vals just make sure the contrast is optimal

+ can combine keyword with fu/op? #4452C4 -> #006893

## Check in

with those changes, here is where I think I am

```{r}
a11y_v2 <- read_theme("a11y_v2.theme")
bg <- "#f8f8f8"
col_v2 <- a11y_v2 %>%
  group_by(fg) %>%
  summarise(abbr = paste(abbr, collapse = "/"), .groups = "drop") %>%
  filter(!is.na(fg)) %>% 
  mutate(contrast = contrast_ratio(fg, bg))

col_v2 %>% plot_uv()

col_v2 %>% plot_cl()

col_v2 %>% 
  arrange(contrast)

plot(prismatic::color(col_v2$fg), labels = TRUE)
```

Compare them
```{r}
library(waldo)
compare(col4, col_v2)
```


# Adjust chroma? 
# ----------------------------------------------------------

```{r}
blend <- function(x, y, delta) {
  x * delta + y * (1 - delta)
}

col5 <- col4 %>%
  mutate(
    fg_before5 = fg,
    fg = modify_hcl(fg, 
                    c = ifelse(c < 1, c, blend(c, 40, 0.4))
                    )
    )
col5 %>% plot_uv()

col5
```


# Colour blindness - experiment
# --------------------------------------------------------
```{r}
col4 %>%
  mutate(fg = prismatic::clr_deutan(fg)) %>%
  plot_uv()


# Alternate between lighter and dark between adjacent hues
# Not very effective
col4 <- col3 %>%
  mutate(hcl(fg)) %>%
  arrange(h) %>%
  mutate(fg = modify_hcl(fg, l = rep(c(20, 50), length.out = nrow(col3))))
col4 %>% plot_uv()

col4 %>%
  mutate(fg = prismatic::clr_deutan(fg)) %>%
  plot_uv()

# Might be better to just switch colours so that the most important
# colours are further apart - e.g. switch bn/fl/dv with dt
```

## Log changes

### Round 1, suggested by Hadley

op -> fu (operators to #4254A7 - cobalt) 

unmerged the above!

pp -> dt (preprocessor to #aa5d00 - a11y chelsea gem)

do -> co (documentation to #545454 - a11y emporer)

cn -> fl (constant to #a1024a - magenta)

unmerged the above!

ss -> st (special string to #008000 - a11y japanese laurel)

er/al -> old cn (errors/alerts to #d91e18 - a11y thunderbird;
functionally replace #ff0000 with #d91e18)

```{r ref.label="col"}

```


### Round 2, added by Alison

at -> st (attribute to #008000 - a11y japanese laurel)

```{r ref.label="col2"}

```

### Round 3, added by Alison (again)

`#545454` -> `#5E5E5E` (an/in/wa/do/co/cv) [replace a11y emporer]

`#007faa` -> `#006893` (ot/cf/kw) [replace a11y deep cerulean]

`#d91e18` -> `#BD1600` (er/al) [replace a11y thunderbird]

`#008000` -> `#006E4C` (at/ss/st/vs/ch/sc) [replace a11y japanese laurel]

`#4254A7` -> `#4452C4` (fu/op) [not a11y]

`#19177c` -> `#??` (va) [not a11y]

`#4452C4` -> `#006893` (fu/op/ot/cf/kw) 

`#BC1500` -> `#B12458` (er/al/pp/dt)

```{r ref.label="col3"}

```




```{r col, include=FALSE}
col4 %>% select(ends_with("2"), abbr)
```

```{r col2, include=FALSE}
col4 %>% select(ends_with("3"), abbr)
```

```{r col3, include=FALSE}
col4 %>% select(ends_with("4"), abbr)
```

```{r col4, include=FALSE}
col4
```

---
## ukekele moon :)

```{r}
ukelele <- tribble(
  ~abbr, ~fg,
  "sky", "#0c2b85",
  "scarf", "#9b1d3d",
  "uke", "#328a75",
  "fox", "#c06b2e",
  "gray", "#727272",
  "teal", "#007faa" 
  ) %>% 
  # adjust luminance
  mutate(
    fg = ifelse(!abbr %in% c("sky", "scarf"), 
                modify_hcl(fg, l = 40), 
                fg),
    contrast = contrast_ratio(fg, bg)
  )

ukelele
plot_uv(ukelele) 
plot(prismatic::color(ukelele$fg), labels = TRUE)

ukelele %>%
  mutate(fg = prismatic::clr_deutan(fg)) %>%
  plot_uv()

ukelele %>%
  mutate(fg = prismatic::clr_greyscale(fg)) %>%
  plot_cl()
```

green 

#006C4A -> uke   #006C57

#954a00 -> scarf #9b1d3d 

#006893 -> kala #006D6F

#4452c4 -> sky   #0c2b85

#5e5e5e -> gray  #5E5E5E (don't change!)

#111 -> fox   #994800 

v1 is distill original

v2 is Hadley edits

v3 is ukelele moon

v4 is variables = black like v2, keep fl = #9b1d3d, but split cn from #9b1d3d -> #994800

v5 is v4, but #0c2b85 -> #4758AB

```{r}
modify_hcl("#4254a7", l = 40)
```

